Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2017-01-06 Manuscript/Manuscript.Rmd
added final contribution plots

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Communicable" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > -0.5), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Communicable"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure7d, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Non-communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Non-communicable"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure7e, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Injuries"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Injuries"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure7f, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "All other causes"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "All other causes"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure8a, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Cancers"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Cancers"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure8b, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Cardiovascular"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Cardiovascular"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure8c, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Communicable"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure8d, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Non-communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Non-Communicable"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure8e, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Injuries"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Injuries"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

@@

```{r figure8f, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "All other causes"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "All other causes"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)
```

>>>>

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Communicable" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Communicable"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure7d, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Non-communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Non-communicable"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Non-communicable" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Non-communicable"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure7e, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Injuries"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "Injuries"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "Injuries" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Injuries"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure7f, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "All other causes"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Male" & Cause.of.death == "All other causes"), aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Male" & Cause.of.death == "All other causes" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "All other causes"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure8a, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Cancers"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Cancers"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Cancers" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Cancers"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure8b, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Cardiovascular"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Cardiovascular"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Cardiovascular" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Cardiovascular"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure8c, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Communicable"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Communicable" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Communicable"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure8d, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Non-communicable"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Non-Communicable"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Non-communicable" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > 0), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Non-communicable"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure8e, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Injuries"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "Injuries"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "Injuries" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > -0.2), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "Injuries"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```

@@

```{r figure8f, fig.align="center", fig.height=8, fig.width=9, echo=F}
ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "All other causes"), aes(x = Year3, y = C_x_COD)) + 
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (years)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2013 & Sex2 == "Female" & Cause.of.death == "All other causes"), 
         aes(label = stabbrs), check_overlap = T, size = 2.5)
)

ggplotly(ggplot(subset(cod.contributions, Sex2 == "Female" & Cause.of.death == "All other causes" & C_x_COD_proportion < 0.5 & C_x_COD_proportion > -0.2), aes(x = Year3, y = C_x_COD_proportion)) +
         geom_line(aes(col = State2)) + facet_wrap(~ Census_Region) +
         ylab("Contribution to LE Gap (%)") +
         xlab("Year") +
         geom_text(data = subset(cod.contributions, Year3 == 2000 & Sex2 == "Male" & Cause.of.death == "All other causes"),
         aes(label = stabbrs), check_overlap = T, size = 2.5))
```
